---
title: "PSTAT 131-HW3"
output: html_document
date: "2022-10-30"
name: "Nathan De Los Santos"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidymodels)
library(ISLR) # For the Smarket data set
library(ISLR2) # For the Bikeshare data set
library(discrim)
library(poissonreg)
library(corrr)
library(klaR) # for naive bayes
tidymodels_prefer()
titanic_data <- read.csv('data/titanic.csv')
```

```{r}
set.seed(222)

titanic_data$pclass <- factor(titanic_data$pclass)
titanic_data$survived <- factor(titanic_data$survived, levels = c("Yes", "No"))
```

## Question 1
```{r}
titanic_split <- initial_split(titanic_data, prop = 0.7, strata = survived)
titanic_train <- training(titanic_split)
titanic_test <- testing(titanic_split)
view(titanic_train)
```
There are missing values within variables such as age and cabin; therefore it is also a good idea to stratify the data so we can get a more precise analysis of the entire dataset

## Question 2
```{r}
titanic_train %>%
  ggplot(aes(survived)) +
  geom_bar()
```
According to the bar graph, we can see that there are more passengers than did not survive than did survive. Roughly, I would say that, in the training set, "No" accounts for about 3/5 of the data and "Yes" takes about 2/5.

## Question 3
```{r}
cor_titanic <- titanic_train %>%
  select(age, fare) %>%
  correlate()
rplot(cor_titanic)
```


## Question 4
```{r}
titanic_recipe <- recipe(survived ~ pclass + sex + age + sib_sp + parch + fare, data = titanic_train) %>% 
  step_impute_linear() %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_interact(terms = ~ sex:fare) %>%
  step_interact(terms = ~ age:fare)
```


## Question 5
```{r}
titanic_reg <- logistic_reg() %>% 
  set_engine("glm") %>% 
  set_mode("classification")

titanic_lin_wkflow <- workflow() %>% 
  add_model(titanic_reg) %>% 
  add_recipe(titanic_recipe)

titanic_lin_fit <- fit(titanic_lin_wkflow, titanic_train)
```


## Question 6
```{r}
titanic_lda <- discrim_linear() %>% 
  set_mode("classification") %>% 
  set_engine("MASS") 

titanic_lda_wkflow <- workflow() %>% 
  add_model(titanic_lda) %>% 
  add_recipe(titanic_recipe)

titanic_lda_fit <- fit(titanic_lda_wkflow, titanic_train)
```


## Question 7
```{r}
titanic_qda <- discrim_quad() %>% 
  set_mode("classification") %>% 
  set_engine("MASS") 

titanic_qda_wkflow <- workflow() %>% 
  add_model(titanic_qda) %>% 
  add_recipe(titanic_recipe)

titanic_qda_fit <- fit(titanic_qda_wkflow, titanic_train)
```


## Question 8
```{r}
titanic_nb <- naive_Bayes() %>% 
  set_mode("classification") %>% 
  set_engine("klaR") %>% 
  set_args(usekernel = FALSE)

titanic_nb_wkflow <- workflow() %>% 
  add_model(titanic_nb) %>% 
  add_recipe(titanic_recipe)

titanic_nb_fit <- fit(titanic_nb_wkflow, titanic_train)
```


## Question 9
```{r}
lin_pred <- predict(titanic_lin_fit, data = titanic_train)
lda_pred <- predict(titanic_lda_fit, data = titanic_train)
qda_pred <- predict(titanic_qda_fit, data = titanic_train)
nb_pred <- predict(titanic_nb_fit, data = titanic_train)

bind_cols(lin_pred, lda_pred, qda_pred, nb_pred)

lin_acc <- augment(titanic_lin_fit, new_data = titanic_train) %>% 
  accuracy(truth = Direction, estimate = .pred_class)
lda_acc <- augment(titanic_lda_fit, new_data = titanic_train) %>% 
  accuracy(truth = Direction, estimate = .pred_class)
qda_acc <- augment(titanic_qda_fit, new_data = titanic_train) %>% 
  accuracy(truth = Direction, estimate = .pred_class)
nb_acc <- augment(titanic_nb_fit, new_data = titanic_train) %>% 
  accuracy(truth = Direction, estimate = .pred_class)
```


## Question 10
```{r}

```